### 2019-07-02 appendices/proofs.tex
Last corrections for camera ready

  \case
    {$\userule{E-Edit}$}
    {Given that $\Gamma,\Sigma\infers\Edit e:\Task \tau$ and $\Sigma\infers s$,\refrule{T-Edit} gives us that $\Gamma,\Sigma\infers e:\tau$.
    The induction hypothesis gives us that $e,s\evaluate v,s'$ also preserves, and thus $\Gamma,\Sigma\infers v:\tau$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers\Edit v:\Task\tau$.}

@@

  \case
    {$\userule{E-Update}$}
    {Given that $\Gamma,\Sigma\infers \Edit e:\Task \tau$ and $\Sigma\infers s$, \refrule{T-Update} gives us that $\Gamma,\Sigma\infers e:\Ref \tau$.
    The induction hypothesis gives us that $e,s\evaluate l,s'$ also preserves, and thus $\Gamma,\Sigma\infers l:\Ref\tau$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers\Update l:\Task\tau$.}

@@

  \case
    {$\userule{E-Then}$}
    {Given that $\Gamma,\Sigma\infers e_1\Then e_2:\Task \tau$ and $\Sigma\infers s$, \refrule{T-Then} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$.
    By the induction hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.}

  \case
    {$\userule{E-Next}$}
    {Given that $\Gamma,\Sigma\infers e_1\Next e_2:\Task \tau$ and $\Sigma\infers s$, \refrule{T-Next} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$.
    By the induction hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$.}

  \case
    {$\userule{E-And}$}
    {Given that $\Gamma,\Sigma\infers e_1\And e_2:\Task(\tau_1\times\tau_2)$ and $\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\Task\tau_2$.
    By the induction hypothesis, we know that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$, $\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau_2$ and $\Sigma\infers s''$.
    Therefore $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$.}

  \case
    {$\userule{E-Or}$}
    {Given that $\Gamma,\Sigma\infers e_1\Or e_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau$ and $\Gamma,\Sigma\infers e_2:\Task\tau$.
    By the induction hypothesis, we have that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau$, $\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau$ and $\Sigma\infers s''$.
    Therefore $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$.}

@@

\begin{lemma}[Task value preserves types]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $\Value{(e,\sigma)}=v$,
  then $v:\tau$.
  \label{lem:presvalue}
\end{lemma}

@@

\case {$\Value{(\Update l,s)}=s(l)$ }
      {Given that $\Gamma,\Sigma\infers\Update l:\Task \tau$ and $\Sigma\infers s$,
      we know that $\Gamma,\Sigma\infers s(l):\tau$ by definiton.}

@@

\begin{lemma}[Striding preserves types]
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $e,\sigma \stride e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\Task\tau$ and $\Sigma \infers \sigma'$.
  \label{thm:pres-stride}
\end{lemma}

@@

  \case{$\userule{N-Done}$}
    {Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by
    \Cref{thm:pres-eval}.
    Then by \cref{thm:pres-stride}, we have $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.}

  \case
    {$\userule{N-Repeat}$}
    { Given that $\Gamma,\Sigma\infers e:\Task\tau$ and $\Sigma\infers s$, we know that $\Gamma,\Sigma\infers t:\Task\tau$ and $\Sigma\infers s'$ by \cref{thm:pres-eval}.
    Then by \cref{thm:pres-stride}, we have $\Gamma,\Sigma\infers t':\Task\tau$ and $\Sigma\infers s''$.
    Then by the induction hypothesis, we finally obtain that $\Gamma,\Sigma\infers t'':\Task\tau$ and $\Sigma\infers s'''$.}

@@

\begin{lemma}
  Given that $\Sigma\infers s$, $\Sigma(l)=\tau$ and $\Gamma,\Sigma\infers v:\tau$, it holds that $\Sigma\infers s[l\mapsto v]$
  \label{lemmasigmaconsistent}
\end{lemma}
This lemma follows immediately from definition.

@@

  \case
    {$\userule{H-Change}$}
    {Given that $\Gamma,\Sigma\infers\Edit v:\Task\tau$ and $\Sigma\infers s$, the \refrule{H-Change} rule additionally gives us that $v,v':\tau$. Therefore by \refrule{T-Edit} we have that $\Gamma,\Sigma\infers\Edit v':\Task\tau$.}

  \case
    {$\userule{H-Fill}$}
    {Given that $\Gamma,\Sigma\infers\Enter\tau$ and $\Sigma\infers s$, the \refrule{H-Fill} rule additionally gives us that $v':\tau$.
    Then by \refrule{T-Enter} we have $\Gamma,\Sigma\infers \Edit v':\Task\tau$.}

  \case
    {$\userule{H-Update}$}
    {Given that $\Gamma,\Sigma\infers\Update l:\Task\tau$ and $\Sigma\infers s$.
    This gives us that $\Sigma(l)=\tau$, and we additionally obtain $s(l),v':\tau$ by \refrule{H-Update}.
    By application of \cref{lemmasigmaconsistent} this case holds.}

  \case
    {$\userule{H-PickLeft}$}
    {Given that $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Sigma\infers s$,
    then by \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_1:\Task \tau$.}

  \case
    {$\userule{H-PickRight}$}
    {Given that $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Sigma\infers s$,
    then by \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_2:\Task \tau$.}

  \case
    {$\userule{H-Next}$}
    {Given that $\Gamma,\Sigma\infers t_1\Next e_2 :\Task\tau$ and $\Sigma\infers s$.
    Then by \refrule{T-Next}, we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
    Then by \refrule{T-Then} we obtain $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.}

  \case
    {$\userule{H-PassThen}$}
    {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$ and $\Sigma\infers s$,
    \refrule{T-Then} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
    By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,Sigma\infers s'$.
    By \refrule{T-Then} we now obtain that $\Gamma,\Sigma\infers t_1'\Then e_2:\Task\tau$.}

\case{$\userule{H-PassNext}$}
     {Given that $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Next} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
     By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,Sigma\infers s'$.
     By \refrule{T-Next} we now obtain that $\Gamma,\Sigma\infers t_1'\Next e_2:\Task\tau$. }

\case{$\userule{H-FirstAnd}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers t_2:\Task\tau_2$.
     By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Sigma\infers s'$.
     Therefore by \refrule{T-Next} we obtain $\Gamma,\Sigma\infers t_1'\And t_2:\Task(\tau_1\times\tau_2)$.}

\case{$\userule{H-SecondAnd}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers t_2:\Task\tau_2$.
     By the induction hypothesis, we know that $t_2,s\handle{i}t_2',s'$ also preserves and thus $\Gamma,\Sigma\infers t_2':\Task\tau_2$ and $\Sigma\infers s'$.
     Therefore by \refrule{T-Next} we obtain $\Gamma,\Sigma\infers t_1\And t_2':\Task(\tau_1\times\tau_2)$.}

\case{$\userule{H-FirstOr}$}
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis we know that $t_1,s\handle{i}t_1',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_1':\Task\tau$ and $\Sigma\infers s'$.
     By \refrule{T-Or} we now obtain $\Gamma,\Sigma\infers t_1'\Or t_2:\Task\tau$.}

\case{$\userule{H-SecondOr}$}
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis we know that $t_2,s\handle{i}t_2',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_2':\Task\tau$ and $\Sigma\infers s'$.
     By T-Or we now obtain $\Gamma,\Sigma\infers t_1\Or t_2':\Task\tau$.}

>>>>

  \case
    {$\userule{E-Edit}$}
    {Given that $\Gamma,\Sigma\infers\Edit e:\Task \tau$ and $\Gamma,\Sigma\infers s$,\refrule{T-Edit} gives us that $\Gamma,\Sigma\infers e:\tau$.
    The induction hypothesis gives us that $e,s\evaluate v,s'$ also preserves, and thus $\Gamma,\Sigma\infers v:\tau$ and $\Gamma,\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers\Edit v:\Task\tau$.}

@@

  \case
    {$\userule{E-Update}$}
    {Given that $\Gamma,\Sigma\infers \Edit e:\Task \tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Update} gives us that $\Gamma,\Sigma\infers e:\Ref \tau$.
    The induction hypothesis gives us that $e,s\evaluate l,s'$ also preserves, and thus $\Gamma,\Sigma\infers l:\Ref\tau$ and $\Gamma,\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers\Update l:\Task\tau$.}

@@

  \case
    {$\userule{E-Then}$}
    {Given that $\Gamma,\Sigma\infers e_1\Then e_2:\Task \tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Then} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$.
    By the induction hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.}

  \case
    {$\userule{E-Next}$}
    {Given that $\Gamma,\Sigma\infers e_1\Next e_2:\Task \tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Next} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1 \to \Task \tau$.
    By the induction hypothesis, we know that $e_1,s\evaluate t_1,s'$ preserves and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers s'$.
    Therefore $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$.}

  \case
    {$\userule{E-And}$}
    {Given that $\Gamma,\Sigma\infers e_1\And e_2:\Task(\tau_1\times\tau_2)$ and $\Gamma,\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\Task\tau_2$.
    By the induction hypothesis, we know that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau_1$, $\Gamma,\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau_2$ and $\Gamma,\Sigma\infers s''$.
    Therefore $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$.}

  \case
    {$\userule{E-Or}$}
    {Given that $\Gamma,\Sigma\infers e_1\Or e_2:\Task\tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers e_1:\Task\tau$ and $\Gamma,\Sigma\infers e_2:\Task\tau$.
    By the induction hypothesis, we have that both $e_1,s\evaluate t_1,s'$ and $e_2,s'\evaluate t_2,s''$ preserve and thus $\Gamma,\Sigma\infers t_1:\Task\tau$, $\Gamma,\Sigma\infers s'$, $\Gamma,\Sigma\infers t_2:\Task\tau$ and $\Gamma,\Sigma\infers s''$.
    Therefore $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$.}

@@

\begin{lemma}[Task value preserves types]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Gamma,\Sigma \infers \sigma$,
  if $\Value{(e,\sigma)}=v$,
  then $v:\tau$.
  \label{lem:presvalue}
\end{lemma}

@@

\case {$\Value{(\Update l,s)}=s(l)$ }
      {Given that $\Gamma,\Sigma\infers\Update l:\Task \tau$ and $\Gamma,\Sigma\infers s$,
      we know that $\Gamma,\Sigma\infers s(l):\tau$ by definiton.}

@@

\begin{lemma}[Striding preserves types]
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Gamma,\Sigma \infers \sigma$,
  if $e,\sigma \stride e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\Task\tau$ and $\Gamma,\Sigma \infers \sigma'$.
  \label{thm:pres-stride}
\end{lemma}

@@

  \case{$\userule{N-Done}$}
    {Given that
    $\Gamma,\Sigma\infers e:\Task\tau$ and $\Gamma,\Sigma\infers s$, we know that $\Gamma,\Sigma\infers t:\Task\tau$ and $\Gamma,\Sigma\infers s'$ by
    \Cref{thm:pres-eval}.
    Then by \cref{thm:pres-stride}, we have $\Gamma,\Sigma\infers t':\Task\tau$ and $\Gamma,\Sigma\infers s''$.}

  \case
    {$\userule{N-Repeat}$}
    { Given that $\Gamma,\Sigma\infers e:\Task\tau$ and $\Gamma,\Sigma\infers s$, we know that $\Gamma,\Sigma\infers t:\Task\tau$ and $\Gamma,\Sigma\infers s'$ by \cref{thm:pres-eval}.
    Then by \cref{thm:pres-stride}, we have $\Gamma,\Sigma\infers t':\Task\tau$ and $\Gamma,\Sigma\infers s''$.
    Then by the induction hypothesis, we finally obtain that $\Gamma,\Sigma\infers t'':\Task\tau$ and $\Gamma,\Sigma\infers s'''$.}

@@

\begin{lemma}
  Given that $\Gamma,\Sigma\infers s$, $\Sigma(l)=\tau$ and $\Gamma,\Sigma\infers v:\tau$, it holds that $\Gamma,\Sigma\infers s[l\mapsto v]$
  \label{lemmasigmaconsistent}
\end{lemma}
This lemma follows immediately from definition.

@@

  \case
    {$\userule{H-Change}$}
    {Given that $\Gamma,\Sigma\infers\Edit v:\Task\tau$ and $\Gamma,\Sigma\infers s$, the \refrule{H-Change} rule additionally gives us that $v,v':\tau$. Therefore by \refrule{T-Edit} we have that $\Gamma,\Sigma\infers\Edit v':\Task\tau$.}

  \case
    {$\userule{H-Fill}$}
    {Given that $\Gamma,\Sigma\infers\Enter\tau$ and $\Gamma,\Sigma\infers s$, the \refrule{H-Fill} rule additionally gives us that $v':\tau$.
    Then by \refrule{T-Enter} we have $\Gamma,\Sigma\infers \Edit v':\Task\tau$.}

  \case
    {$\userule{H-Update}$}
    {Given that $\Gamma,\Sigma\infers\Update l:\Task\tau$ and $\Gamma,\Sigma\infers s$.
    This gives us that $\Sigma(l)=\tau$, and we additionally obtain $s(l),v':\tau$ by \refrule{H-Update}.
    By application of \cref{lemmasigmaconsistent} this case holds.}

  \case
    {$\userule{H-PickLeft}$}
    {Given that $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Gamma,\Sigma\infers s$,
    then by \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_1:\Task \tau$.}

  \case
    {$\userule{H-PickRight}$}
    {Given that $\Gamma,\Sigma\infers t_1\Xor t_2:\Task\tau$ and $\Gamma,\Sigma\infers s$,
    then by \refrule{T-Xor} we have $\Gamma,\Sigma\infers t_2:\Task \tau$.}

  \case
    {$\userule{H-Next}$}
    {Given that $\Gamma,\Sigma\infers t_1\Next e_2 :\Task\tau$ and $\Gamma,\Sigma\infers s$.
    Then by \refrule{T-Next}, we have $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
    Then by \refrule{T-Then} we obtain $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$.}

  \case
    {$\userule{H-PassThen}$}
    {Given that $\Gamma,\Sigma\infers t_1\Then e_2:\Task\tau$ and $\Gamma,\Sigma\infers s$,
    \refrule{T-Then} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
    By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,Sigma\infers s'$.
    By \refrule{T-Then} we now obtain that $\Gamma,\Sigma\infers t_1'\Then e_2:\Task\tau$.}

\case{$\userule{H-PassNext}$}
     {Given that $\Gamma,\Sigma\infers t_1\Next e_2:\Task\tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Next} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers e_2:\tau_1\to\Task\tau$.
     By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,Sigma\infers s'$.
     By \refrule{T-Next} we now obtain that $\Gamma,\Sigma\infers t_1'\Next e_2:\Task\tau$. }

\case{$\userule{H-FirstAnd}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Gamma,\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers t_2:\Task\tau_2$.
     By the induction hypothesis, we know that $t_1,s\handle{i}t_1',s'$ also preserves and thus $\Gamma,\Sigma\infers t_1':\Task\tau_1$ and $\Gamma,\Sigma\infers s'$.
     Therefore by \refrule{T-Next} we obtain $\Gamma,\Sigma\infers t_1'\And t_2:\Task(\tau_1\times\tau_2)$.}

\case{$\userule{H-SecondAnd}$}
     {Given that $\Gamma,\Sigma\infers t_1\And t_2:\Task(\tau_1\times\tau_2)$ and $\Gamma,\Sigma\infers s$, \refrule{T-And} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau_1$ and $\Gamma,\Sigma\infers t_2:\Task\tau_2$.
     By the induction hypothesis, we know that $t_2,s\handle{i}t_2',s'$ also preserves and thus $\Gamma,\Sigma\infers t_2':\Task\tau_2$ and $\Gamma,\Sigma\infers s'$.
     Therefore by \refrule{T-Next} we obtain $\Gamma,\Sigma\infers t_1\And t_2':\Task(\tau_1\times\tau_2)$.}

\case{$\userule{H-FirstOr}$}
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis we know that $t_1,s\handle{i}t_1',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_1':\Task\tau$ and $\Gamma,\Sigma\infers s'$.
     By \refrule{T-Or} we now obtain $\Gamma,\Sigma\infers t_1'\Or t_2:\Task\tau$.}

\case{$\userule{H-SecondOr}$}
     {Given that $\Gamma,\Sigma\infers t_1\Or t_2:\Task\tau$ and $\Gamma,\Sigma\infers s$, \refrule{T-Or} gives us that $\Gamma,\Sigma\infers t_1:\Task\tau$ and $\Gamma,\Sigma\infers t_2:\Task\tau$.
     By the induction hypothesis we know that $t_2,s\handle{i}t_2',s'$ also preserves, and therefore $\Gamma,\Sigma\infers t_2':\Task\tau$ and $\Gamma,\Sigma\infers s'$.
     By T-Or we now obtain $\Gamma,\Sigma\infers t_1\Or t_2':\Task\tau$.}
